---
title: "Heatmap"
output: html_document
date: "2023-10-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Here is a list of libraries to load. Some are used, some aren't. 
```{r}
library(ggplot2)
library(viridis)
library(dplyr)
library(hrbrthemes)
library(latticeExtra)
library(tibble)
library(colorBlindness)
library(reshape2)
```

Upload the data
```{r}
a <- read.csv("RNonBinary.csv") 
```

We need to reorder the Conditions so that when they appear on the graph, they are not randomly listed but appear in the list below
```{r}
a$Condition <- factor(a$Condition, levels = c("pH3","pH9", "4C", "15C", "22C", "30C", "37C", "6%", "9%", "12%", "G", "N", "X" ) )
```

Here is the Heatmap for the data. 
I used reddish-pink because it's the color of our colonies and because I read that contrasting brightness (a light color and a dark color) is best for people who are colorblind. 
```{r}
ggplot(a, aes(SPECIES, Condition, fill= Growth)) + 
  geom_tile()+ #let's make it a heatmap 
  scale_fill_gradient(low = "#FFFFFF",
                    high = "#E57367",
                    guide = "colorbar")+  #here's the colors that we used 
  labs(title = "Heatmap of Strains", 
       x = "Species", 
       y = "Condition")+ #here's the x and y axis title 
   theme(axis.text.x = element_text(angle = 45, hjust=1.0, vjust = 1), plot.title = element_text(hjust = 0.5), plot.margin = margin(10, 10, 10, 100)) #the x axis labels needed to be rotated 45 degrees, the title needed to be centered, and the margin needed to be moved over to as not cut off text 
```

